Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-09-03 ms.tex
More background on detector fundamentals.

\section{A Primer on Detector Operation}
\textcolor{red}{\textbf{NOTE: This section needs checking for factual accuracy by a detector expert}}
It is helpful to review the basic operation of a NIRCam detector in order to understand the systematics affecting time series.
Figure \ref{fig:npSchematic} shows a schematic of an NP semiconductor junction for a H2RG detector from \citet{smith2008imgPersistence}.
The crystalline HgCdTe structure has 4 valence electrons that form covalent bonds in a tetrahedral structure.
By varying the relative amount of Hg, Cd an Te (doping), it is possible to increase or decrease the number of electrons to create mobile charge carriers that moving along the crystaline lattice.
The N-type semiconductor is a negatively-doped HgCdTe crystalline structure that has negative charge carriers (electrons).
The P-type semiconductor is a positively-doped HgCdTe crystalline structure that has positive charge carriers (vacant holes in the lattice structure than can move like electrons).

@@

The junction of these two materials enables electrons to flow from the N-type material to the P-type material where it can complete a valence shell in the semiconductor material.
This produces a negative charge on the P-type side.
Conversely, the positively charged holes from the P-type material flow to the N-type material to complete the valence shell and this produces a positive charge.
In the region where electrons have completed the valence shells in the P-type material and holes in the N-type material, the valence shells are complete.
This region spanning across the two semiconductor materials is called the depletion region.
The positive net charge on the N-type material and negative charge in the P-type material causes a voltage (potential) difference across the detector that can be measured with an amplifier.

Furthermore, the junction is ``reverse-biased'' with a positive potential on the N-type material and negative potential on the P-type material to draw more electrons.
The reverse bias causes more charge carriers to flow across the NP junction and this increases the size of the depletion region, which also increases the well depth or capacity of electrons that the detector may collect before saturation.
The reverse bias is applied 
Figure \ref{fig:npSchematic} shows the case where the density of charge carriers is equal in the N-type and P-type semiconductors, but in reality, the density of In reality, the physical size of the P-type semiconductor is much smaller than the N-type and the N-type is responsible for detecting photons.

Note that Figure \ref{fig:npSchematic} shows the mobile charge carriers only, so the depletion region, with no mobile charges is positively charged on the N-type side and negatively charged on the P-type side.
The undepleted region is electrically neutral because the nuclei of the N-type material have an equal number of extra protons as the negatively charged electrons.
Similarly, the undepleted region of the P-type semiconductor has fewer protons in its atomic nuclei producing an overall neutral charge.
Textbook NP junction schematics usually show the net charge and thus symbolize the regions with charge carriers as empty and the depletion region with ``+'' symbols on the N-type semiconductor and ``-'' symbols on the P-type˚.

When an incoming photon hits the (check if this is correct) n-type depletion region, it will excite the hole to a higher energy level and this will return it to the P-type side.
A second photon will excite another hole from the N-side that causes it to flow to the P side.
This continues and depletes the size of the depletion region until there is a smaller charge difference across the NP junction.

produce a negatively charged region on the P-type conductor. positive and negative charge carriers to join as completed valence electron shells in the lattice.

>>>>

\section{A Primer on Detector Operation}
\textcolor{red}{\textbf{NOTE: This section needs checking for factual accuracy by a detector expert}}
It is helpful to review the basic operation of a NIRCam detector in order to understand the systematics affecting time series.
Figure \ref{fig:npSchematic} shows a schematic of an NP semiconductor junction for a H2RG detector from \citet{smith2008imgPersistence}.
The crystalline HgCdTe structure has 4 valence electrons that form covalent bonds in a tetrahedral structure.
By varying the relative amount of Hg, Cd an Te (doping), it is possible to increase or decrease the number of electrons to create mobile charge carriers that moving along the crystaline lattice.
The N-type semiconductor is a negatively-doped HgCdTe crystalline structure that has negative charge carriers (electrons) .
The P-type semiconductor is a positively-doped HgCdTe crystalline structure that has positive charge carriers (vacant holes in the lattice structure than can move like electrons).

@@

The junction of these two materials enables electrons to flow from the N-type material to the P-type material where it can complete a valence shell in the semiconductor material.
This produces a negative charge on the P-type side.
Conversely, the positively charged holes from the P-type material flow to the N-type material to complete the valence shell and this produces a positive charge.
This difference is called the contact potential.
In the region where electrons have completed the valence shells in the P-type material and holes in the N-type material, the valence shells are complete.
This region spanning across the two semiconductor materials is called the depletion region, because it contains no mobile charge carriers.
The positive net charge on the N-type material and negative charge in the P-type material causes a voltage (potential) difference across the detector.

Furthermore, the junction is ``reverse-biased'' with a positive potential on the N-type material and negative potential on the P-type material to draw more electrons.
The reverse bias reduces the number of mobile charge carriers and increases the size of the depletion region, which also increases the well depth or capacity of electrons that the detector may collect before saturation.
The reverse bias is applied at each reset at the beginning of a detector's integration (\textbf{Check!}).
Figure \ref{fig:npSchematic} shows the case where the density of charge carriers is equal in the N-type and P-type semiconductors, but in reality, the density of the P-type semiconductor is much higher than the N-type, so the depletion region has a larger physical size on the N-type side.

Note that Figure \ref{fig:npSchematic} shows the mobile charge carriers only, so the depletion region, with no mobile charges is positively charged on the N-type side and negatively charged on the P-type side.
The undepleted region is electrically neutral because the nuclei of the N-type material have an equal number of extra protons as the negatively charged electrons.
Similarly, the undepleted region of the P-type semiconductor has fewer protons in its atomic nuclei producing an overall neutral charge \citep[e.g.][]{halliday2004physicsText}.
Textbook NP junction schematics often show the net charge and thus symbolize the regions with charge carriers as empty and the depletion region with ``+'' symbols on the N-type semiconductor and ``-'' symbols on the P-type˚.
The schematic in Figure \ref{fig:npSchematic} instead shows the mobile charge carriers as ``+'' and ``-'' because it is easier to understand the charge trapping effect \citep[e.g.][]{smith2008imgPersistence}.

When an incoming photon hits the (check if this wording is correct) n-type depletion region, it will excite an electron from the valence to conduction band which creates an electron-hole pair \citep{rieke2007irDetectorReview}.
The electron moves to the extremity of the depletion zone in the N-type material whereas the positive hole generated crosses the NP junction and adds a mobile charge to the P-type side.
The incoming photon has the effect of increasing the size of the depletion region.
A second photon will excite another hole from the N-side that causes it to flow to the P side.
This continues and depletes the size of the depletion region until there is a smaller charge difference across the NP junction.
The diffusion of charge carriers across the junction creates an electric current that can be measured in a circuit.
(\textbf{Why does the literature refer to the current, as opposed to the voltage? I thought you measure a voltage and then reset? Is this the gate voltage?})

As the size of the depletion region decreases, the detector becomes decreasingly sensitive to new photons.
Thus, the NIRCam HgCdTe detectors are never strictly linear.
Eventually, with enough photons, the depletion region is too small to create electron-hole pairs with incoming photons.
This is where the detector approaches saturation and no longer changes voltage with more light.

A sensitive amplifier converts the measured voltage potential into a signal.
The electronic circuit that digitizes the voltages is tuned to ensure the 16 bits (65,536 possible Data numbers) measure the voltage across the NP junction from the value just after reset before photons are detected all the way to saturation where the maximum number of photons are collected.
The minimum voltage is several thousands of counts above zero to ensure that changes in the bias signal do not below 0.
The 16,536 DN level is tuned to be just above the HgCdTe full well capacity to measure full saturation.

\subsection{Charge Trapping}
